Project 2

### 2021-10-15 project_2.Rmd
.

```{r fitzgerald_emotion_table}
#counting how often female words appeared
#table shows each text and the respective percentage
fitzgerald_emotion_calc <- fitzgerald_emotions %>% group_by(title) %>% count(emotion) %>% mutate(percent = n/sum(n)*100) %>% mutate(author = "F. Scott Fitzgerald")

@@

```{r hemingway_emotion_table}
#counting how often female words appeared
#table shows each text and the respective percentage
hemingway_emotion_calc <- hemingway_emotions %>% group_by(title) %>% count(emotion) %>% mutate(percent = n/sum(n)*100) %>% mutate(author = "Earnest Hemingway")

>>>>

```{r fitzgerald_emotion_table}
#counting how often female words appeared
#table shows each text and the respective percentage
fitzgerald_emotion_calc <- fitzgerald_emotions %>% group_by(title) %>% count(emotion) %>% mutate(percent = round(n/sum(n)*100, 2)) %>% mutate(author = "F. Scott Fitzgerald")

@@

```{r hemingway_emotion_table}
#counting how often female words appeared
#table shows each text and the respective percentage
hemingway_emotion_calc <- hemingway_emotions %>% group_by(title) %>% count(emotion) %>% mutate(percent = round(n/sum(n)*100, 2)) %>% mutate(author = "Earnest Hemingway")
